Rapid, (semi-?)Supervised Generation of Novel Percussive Sounds With A Tractable Virtual Synthesizer

### 2020-01-03 paper.tex
Updates from Overleaf

\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-c}
\includegraphics[width=0.48\linewidth]{example-image-c}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
\label{fig:evo-graphs}
\end{figure}
\subsubsection{Survey of Generated Drums}
\label{survey}
\colorbox{green!=30}{Finalize ear,generate,make survey.} The survey will be sent out. I know a few producers who are willing to do this.
3 algorithms, 3 categories, 10 samples for each algorithm and category pair, 2 seconds to listen to each sample-> 3 minutes for listening
I imagine survey will be around 5-6 minutes long.
\subsubsection{Contrasting Ear Scores With Survey Results}
\colorbox{green!=30}{pending section \ref{survey}}
\section{Code and Database}
\colorbox{green!=30}{One last thing to do, will take a 1 day}\\
\colorbox{blue!=30}{Should this section be at the start of the paper?Appendix?}\\
talk about  categories, sources, dataprocessing. 
Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
Give link for people to download it, show where to find the scripts for database expansion.
\section{Summary and Conclusions}
\colorbox{green!=30}{Points I want to make:}
\begin{itemize}
    \item Our methodology was successful in generating novel examples of some percussion categories.
    \item With the right implementation of DSP methods to create a synth, Genetic search is viable for finding  desired programs and parameters.
    \item When possible, using DSP methods instead of NNs is preferable in many ways(speed,computation,hardware requirements).\\
    \colorbox{green!=30}{Include some speed measurements in appendix?}
    \item ...
\end{itemize}
\section{Future Work}
\colorbox{blue!=30}{Should really think this through}
\begin{itemize}
    \item Potential for other generative methods (e.g reinforcement learning)
    \item Making the synth's sound range more diverse while maintaining speed and efficiency
\end{itemize}
\bibliographystyle{abbrv}
    \bibliography{nime-references} 
\end{document}

>>>>

\begin{figure}[H]
\centering
\begin{subfigure}[b]{\linewidth}
\includegraphics[width=0.48\linewidth]{example-image-c}
\includegraphics[width=0.48\linewidth]{example-image-c}
\label{fig:1stack}
\setcounter{subfigure}{2}%
\end{subfigure}
\caption{\colorbox{green!=40}{todo}Graphs showing the effectiveness of this method for producing chosesn categories in under a minute}
\label{fig:evo-graphs}
\end{figure}
\subsubsection{Survey of Generated Drums}
\label{survey}
\colorbox{green!=30}{Finalize ear,generate,make survey.} The survey will be sent out. I know a few producers who are willing to do this.
3 algorithms, 3 categories, 10 samples for each algorithm and category pair, 2 seconds to listen to each sample-> 3 minutes for listening\\
With those numbers I imagine survey will be around 5-6 minutes long.
\subsubsection{Contrasting Ear Scores With Survey Results}
\colorbox{green!=30}{pending section \ref{survey}}
\section{Code and Database}
\colorbox{green!=30}{One last thing to do, will take a 1 day}\\
\colorbox{blue!=30}{Should this section be at the start of the paper?Appendix?}\\
talk about  categories, sources, data processing. 
Code for the data processing is written, I need to download the no-copyright sounds, run the code and host the results. 
Give link for people to download it, show where to find the scripts for database expansion.
\section{Summary and Conclusions}
\colorbox{green!=30}{Points I want to make:}
\begin{itemize}
    \item Our methodology was successful in generating novel examples of some percussion categories.
    \item With the right implementation of DSP methods to create a synth, Genetic search is viable for finding  desired programs and parameters.
    \item When possible, using DSP methods instead of NNs is preferable in many ways(speed,computation,hardware requirements).\\
    \colorbox{green!=30}{Include some speed measurements in appendix?}
    \item ...
\end{itemize}
\section{Future Work}
\colorbox{blue!=30}{Need to think about this more}
\begin{itemize}
    \item Potential for other generative methods (e.g reinforcement learning)
    \item Making the synth's sound range more diverse while maintaining speed and efficiency
    \item Can our approach be used for VSTs?
\end{itemize}
%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.
\section{Ethical Standards}
To ensure objectivity and transparency in research and to ensure that accepted principles of ethical and professional conduct have been followed, authors should include a section “Ethical Standards” before the References, including (if relevant): information regarding sources of funding, potential conflicts of interest (financial or non-financial), informed consent if the research involved human participants, statement on welfare of animals if the research involved animals.

\appendix
%Appendix A
\section{section A}
In case I need an appendix
\subsection{Example Subsection}
\section{Section B}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments

%%% Place this com
\bibliographystyle{abbrv}
    \bibliography{nime-references} 
\end{document}
